Racial and Ethnic Differences in ETI: Outcomes

### 2024-08-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
weord table formatting

```{r results='asis'}
#| message: false
invisible(lapply(continuous_outcomes[1:3], function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + age_group + Insurance + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  cat("### Model results")
  cat("\n")
  cat("\n")
  m %>%
    tbl_regression() %>%
    print()
  cat("\n")
  cat("\n")
  # Plot
  cat("\n")
  cat("\n")
  cat("## Model predictions")
  cat("\n")
  cat("\n")
  pred <- predict_response(m, terms = c("Days[-1095,0,730]", "Race"))
  pred %>% print()
  cat("\n")
  cat("\n")
  cat("### Plot")
  cat("\n")
  cat("\n")
  pred %>%
    plot() %>%
    print()
  cat("\n")
  cat("\n")
}))
```

>>>>

```{r results='asis'}
#| message: false
invisible(lapply(continuous_outcomes[1:3], function(o) {
  # Formula
  f <-
    as.formula(paste0(
      o,
      "~ bs(Days, knots = 0, degree = 1) * Race + age_group + Insurance + (1 | eDWID)"
    ))
  m <- lmer(f, data = encounter)
  # Print table
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  cat("### Model results")
  cat("\n")
  cat("\n")
  m %>%
    tbl_regression() %>%
    print()
  cat("\n")
  cat("\n")
  # Plot
  cat("\n")
  cat("\n")
  cat("## Model predictions")
  cat("\n")
  cat("\n")
  pred <- predict_response(m, terms = c("Days[-1095,0,730]", "Race"))
  pred %>% gt() %>% print()
  cat("\n")
  cat("\n")
  cat("### Plot")
  cat("\n")
  cat("\n")
  pred %>%
    plot() %>%
    print()
  cat("\n")
  cat("\n")
}))
```
